\LARGE \bf Informed sampling by Markov Chain Monte Carlo methods

### 2017-09-12 paper.tex
sync

@@

\begin{figure*}[t!]
	\centering
	\begin{subfigure}[b]{\textwidth}
	    \centering
		\includegraphics[height=3cm]{fig/planning_efficiency/3dof_example}
		\includegraphics[height=3cm]{fig/planning_efficiency/3dof_example}
		\includegraphics[height=3cm]{fig/planning_efficiency/3dof_example}
		\includegraphics[height=3cm]{fig/planning_efficiency/3dof_example}
		\caption{3DOF planar}
		\label{fig:planning_efficiency:3dof:example}
	\end{subfigure}
	\begin{subfigure}[b]{\textwidth}
	    \centering
		\includegraphics[height=3cm]{fig/planning_efficiency/6dof_example}
		\includegraphics[height=3cm]{fig/planning_efficiency/6dof_example}
		\includegraphics[height=3cm]{fig/planning_efficiency/6dof_example}
		\includegraphics[height=3cm]{fig/planning_efficiency/6dof_example}
		\caption{6DOF snake}
		\label{fig:planning_efficiency:6dof:example}
	\end{subfigure}
	\begin{subfigure}[b]{\textwidth}
    \centering
    \includegraphics[height=3cm]{fig/planning_efficiency/6dof_example}
	\caption{HERB}
	\label{fig:planning_efficiency:6dof:example}
	\end{subfigure}
	\caption{Test problems to evaluate planning efficiency. TODO: Add herb and update figures}
	\label{fig:problems}
\end{figure*}

\begin{figure}[t!]
	\centering
	\begin{subfigure}[b]{0.5\textwidth}
		\includegraphics[width=\linewidth]{fig/planning_efficiency/3dof_general}
		\caption{\captionstyle Planning Efficiency for Problem 1: 3 DoF Manipulator}
		\label{fig:planning_efficiency:3dof:general}
	\end{subfigure}	
% 	\begin{subfigure}[b]{0.5\textwidth}
% 		\includegraphics[width=\linewidth]{fig/planning_efficiency/3dof_hammering}
% 		\caption{Hammering}
% 		\label{fig:planning_efficiency:3dof:hammering}
% 	\end{subfigure}
% 	\begin{subfigure}[b]{0.5\textwidth}
% 		\includegraphics[width=\linewidth]{fig/planning_efficiency/6dof_general}
% 		\caption{Obstacle avoiding}
% 		\label{fig:planning_efficiency:6dof:general}
% 	\end{subfigure}	
	\begin{subfigure}[b]{0.5\textwidth}
		\includegraphics[width=\linewidth]{fig/planning_efficiency/6dof_hammering}
		\caption{Planning Efficiency for Problem 2: 6DoF Hammering Task}
		\label{\captionstyle An example of a 6DOF 3D snake.}
	\end{subfigure}
	\caption{Planning Efficiency}
	\label{fig:planning_efficiency}
\end{figure}

>>>>

\section{Evaluation}

@@

\begin{figure*}[t!]
	\centering
	\begin{subfigure}[b]{\textwidth}
	    \centering
		\includegraphics[height=2.7cm]{fig/planning_efficiency/3dof_1}
		\includegraphics[height=2.7cm]{fig/planning_efficiency/3dof_2}
		\includegraphics[height=2.7cm]{fig/planning_efficiency/3dof_3}
		\includegraphics[height=2.7cm]{fig/planning_efficiency/3dof_4}
		\includegraphics[height=2.7cm]{fig/planning_efficiency/3dof_5}
		\caption{3DOF planar}
		\label{fig:planning_efficiency:3dof:example}
	\end{subfigure}
	\begin{subfigure}[b]{\textwidth}
	    \centering
		\includegraphics[height=3cm]{fig/planning_efficiency/6dof_1}
		\includegraphics[height=3cm]{fig/planning_efficiency/6dof_2}
		\includegraphics[height=3cm]{fig/planning_efficiency/6dof_3}
		\includegraphics[height=3cm]{fig/planning_efficiency/6dof_4}
		\includegraphics[height=3cm]{fig/planning_efficiency/6dof_5}
		\caption{6DOF snake}
		\label{fig:planning_efficiency:6dof:example}
	\end{subfigure}
	\begin{subfigure}[b]{\textwidth}
    \centering
    \includegraphics[height=2.7cm]{fig/planning_efficiency/herb_batting_1}
    \includegraphics[height=2.7cm]{fig/planning_efficiency/herb_batting_2}
    \includegraphics[height=2.7cm]{fig/planning_efficiency/herb_batting_3}
    \includegraphics[height=2.7cm]{fig/planning_efficiency/herb_batting_4}
    \includegraphics[height=2.7cm]{fig/planning_efficiency/herb_batting_5}
	\caption{HERB}
	\label{fig:planning_efficiency:herb:example}
	\end{subfigure}
	\caption{Test problems to evaluate planning efficiency. TODO: Add herb and update figures}
	\label{fig:problems}
\end{figure*}

\begin{figure}[t!]
	\centering
	\begin{subfigure}[b]{0.5\textwidth}
		\includegraphics[width=\linewidth]{fig/planning_efficiency/3dof_general}
		\caption{\captionstyle Planning Efficiency for Problem 1: 3 DoF Manipulator}
		\label{fig:planning_efficiency:3dof:general}
	\end{subfigure}	
	\begin{subfigure}[b]{0.5\textwidth}
		\includegraphics[width=\linewidth]{fig/planning_efficiency/6dof_hammering}
		\caption{\captionstyle Planning Efficiency for Problem 2: 6DoF Hammering Task}
		\label{fig:planning_efficiency:6dof:hammering}
	\end{subfigure}
	\begin{subfigure}[b]{0.5\textwidth}
	\includegraphics[width=\linewidth]{fig/planning_efficiency/herb_batting_efficiency}
	\caption{\captionstyle Planning Efficiency for Problem 3: 7DoF HERB Batting Task}
	\label{fig:planning_efficiency:herb:batting}
    \end{subfigure}
	\caption{Planning Efficiency}
	\label{fig:planning_efficiency}
\end{figure}
